### 2023-05-18 manuscript.tex
more on EOSC IF [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/d023a0b7859ad2f63bd2b2fe25943b6c268c9733.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/d023a0b7859ad2f63bd2b2fe25943b6c268c9733/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5016916629

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/55b211690e436edabc36739a1bca1546f2b6d680/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/55b211690e436edabc36739a1bca1546f2b6d680}{stain/2022-fdo-paper@55b2116}
on May 18, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/d023a0b7859ad2f63bd2b2fe25943b6c268c9733/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/d023a0b7859ad2f63bd2b2fe25943b6c268c9733}{stain/2022-fdo-paper@d023a0b}
on May 18, 2023.
